Oral contraceptives

### 2021-01-08 r_notebooks/exploring_oral_contraceptives.Rmd
adding latent trajectory analyses to oc

```{r}
library(tidyLPA)
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
    estimate_profiles(1:5,
                      variances = c("equal", "varying"),
                      covariances = c("zero", "varying")
                      ) %>% 
    compare_solutions(statistics = c("AIC", "BIC"))
```

@@

>>>>

```{r, eval = FALSE}
library(tidyLPA)
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
    estimate_profiles(1:5,
                      variances = c("equal", "varying"),
                      covariances = c("zero", "varying")
                      ) %>% 
    compare_solutions(statistics = c("AIC", "BIC"))
```

@@

```{r}
best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = (n - .mean), # Why are the numbers so small?
         regional_unit = as.factor(regional_unit)) %>% 
  select(regional_unit, datename, discrepancy) %>% 
  filter(!is.na(discrepancy)) %>% # need to remove NA before pivoting to enalable values_fill
  pivot_wider(names_from = datename, values_from = discrepancy, values_fill = -999) %>% 
  left_join(select(gp, c(practiceid, cluster)), by = c("regional_unit" = "practiceid")) %>% 
  mutate(regional_unit = as.factor(regional_unit),
         cluster = as.factor(cluster)) %>% 
  mutate(regional_unit = as.numeric(regional_unit),
         cluster = as.numeric(cluster)) %>% 
  select(cluster, regional_unit, everything()) %>% 
  write_csv(file = "../data/mplus/oc_gp_discrep.csv", col_names = FALSE)

```{r}
source("../r_scripts/functions/mplus_plotting.R")
mplus.view.plots("../mplus_analyses/oc_gp/oac_discrep_3_class_bayes.gh5")
mplus.plot.estimated_means("../mplus_analyses/oc_gp/oac_discrep_3_class_bayes.gh5")
```
